Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-09-25 paper/meg_exps.tex
modifs

We compare B2B to four standard methods: Forward regression, Backward regression, CCA and PLS, as implemented in scikit-learn \citep{scikit}, and optimized with nested cross validation over twenty $l2$ regularization parameters logarithmically spaced between $10^{-4}$ and $10^4$ (for regression methods) or 1 to 4 canonical components (for cross-decomposition methods).

@@

    \label{fig:meg_results}
  \end{center}
  \caption{Multiple models (color-coded) are compared on their ability to reliably predict single-trial MEG signals evoked by words. Left. Average improvement of correlation coefficient $\Delta R$ for each pf the four features (rows). Error bars indicate standard error of the mean (SEM) across subjects. Right. Average $\Delta R$ across time for each subject (dot). Top horizontal lines indicate when B2B significantly outperform other methods.}
  \vspace{-9ex}
\end{wrapfigure}

@@

To assess which model would be most sensitive to these causal discoveries, we compared B2B to other models across subjects (Figure \ref{fig:meg} right). For Word Length B2B outperforms all models (all $p < 0.00001$) but CCA ($p=0.0678$). For Word Frequency, B2B outperforms all models (all $p < 0.0006$). For "Word Function", B2B outperforms all models (all $p < 0.0015$). Overall, these results show that B2B reliably outperform standard methods, especially when the effects are difficult to detect.

>>>>

We compare B2B to four standard methods: Forward regression, Backward regression, CCA and PLS, as implemented in scikit-learn \citep{sklearn}, and optimized with nested cross validation over twenty $l2$ regularization parameters logarithmically spaced between $10^{-4}$ and $10^4$ (for regression methods) or 1 to 4 canonical components (for cross-decomposition methods).

@@

    \label{fig:meg_results}
  \end{center}
  \caption{Multiple models (color-coded) are compared on their ability to reliably predict single-trial MEG signals evoked by words. Left. Average improvement of correlation coefficient $\Delta R$ for each of the four features (rows). Error bars indicate standard error of the mean (SEM) across subjects. Right. Average $\Delta R$ across time for each subject (dot). Top horizontal lines indicate when B2B significantly outperforms other methods.}
  \vspace{-9ex}
\end{wrapfigure}

@@

To assess which model would be most sensitive to these causal discoveries, we compared B2B to other models across subjects (Figure \ref{fig:meg_results} right). For Word Length B2B outperforms all models (all $p < 0.00001$) but CCA ($p=0.0678$). For Word Frequency, B2B outperforms all models (all $p < 0.0006$). For "Word Function", B2B outperforms all models (all $p < 0.0015$). Overall, these results show that B2B reliably outperform standard methods, especially when the effects are difficult to detect.

### 2019-09-25 paper/synthetic.tex
modifs

We compare the performance of B2B against four competing methods, all
implemented in scikit-learn \citep{scikit}:
%
% To be updated

@@

We employ $5$-fold cross-validation to select the optimal number of components
for CCA and PLS. Regressions were $\ell2$-regularized with a $\lambda$ regularization
parameters fitted with the efficient leave-one-out procedure implemented in
scikit-learn RidgeCV \citep{scikit}.

@@

We report AUC results in Figures~\ref{fig:auc_plots}~(left) and ~\ref{fig:percondition}~(top, in Appendix), and compare favorably to all baselines.

>>>>

We compare the performance of B2B against four competing methods, all
implemented in scikit-learn \citep{sklearn}:
%
% To be updated

@@

We employ $5$-fold cross-validation to select the optimal number of components
for CCA and PLS. Regressions were $\ell2$-regularized with a $\lambda$ regularization
parameters fitted with the efficient leave-one-out procedure implemented in
scikit-learn RidgeCV \citep{sklearn}.

@@

We report AUC results in Figures~\ref{fig:percondition}~(top) and ~\ref{fig:auc_plots}~(left, in Appendix), and compare favorably to all baselines.
